The following design requirements guided the implementation of LLVManim:

\begin{itemize}
  \item \textbf{Simple CLI:} A command-line interface that accepts \texttt{.ll} files, selects visualization options via flags, and produces output with minimal configuration.

  \item \textbf{LLVM IR Parsing:} Extraction of control flow, memory operations, and SSA value information from LLVM IR using the \texttt{llvmlite}\cite{llvmlite} Python binding.

  \item \textbf{Multiple Animation Modes:} Several rendering modes offering different levels of detail---from a compact stack-only view to a full three-column layout showing IR source, SSA values, and the call stack simultaneously.

  \item \textbf{IR Instruction Coverage:} Support for the most common LLVM IR instructions (\texttt{alloca}, \texttt{load}, \texttt{store}, \texttt{call}, \texttt{ret}, \texttt{br}, binary operations, and comparisons), enabling visualization of a wide range of programs.

  \item \textbf{Machine-Readable Export:} JSON scene graph and Graphviz DOT output for integration with external tools and downstream analysis.

  \item \textbf{Testability and Quality:} A comprehensive automated test suite and multi-stage quality gate to maintain correctness throughout development.
\end{itemize}

\textbf{Deliverables:}
\begin{itemize}
  \item A command-line tool that accepts LLVM IR as input and produces animations, DOT graphs, or JSON scene data as output.
  \item A library of reusable Manim scene components for visualizing control flow and stack operations.
  \item Sample visualizations demonstrating LLVManim on standard test programs.
  \item Documentation covering installation, usage, CLI flags, and supported IR constructs.
  \item A test suite of 302 automated tests with 84\% line coverage.
\end{itemize}
