\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{bookmark}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\graphicspath{ {./images/} }

\newcommand{\TODO}[1]{\textbf{TODO (#1): }}

\begin{document}

\title{Presentable Debugging with LLVManim}

\author{\IEEEauthorblockN{Benjamin Houle}
\IEEEauthorblockA{\textit{Dept. of Computer Science} \\
\textit{University of Massachusetts Lowell}\\
Lowell, Massachusetts, USA \\
benjamin\_houle@student.uml.edu}
\and
\IEEEauthorblockN{Name Surname}
\IEEEauthorblockA{\textit{Dept. of Computer Science} \\
\textit{University of Massachusetts Lowell}\\
Lowell, Massachusetts, USA \\
email address or ORCID}
\and
\IEEEauthorblockN{Name Surname}
\IEEEauthorblockA{\textit{Dept. of Computer Science} \\
\textit{University of Massachusetts Lowell}\\
Lowell, Massachusetts, USA \\
email address or ORCID}
\and
\IEEEauthorblockN{Name Surname}
\IEEEauthorblockA{\textit{Dept. of Computer Science} \\
\textit{University of Massachusetts Lowell}\\
Lowell, Massachusetts, USA \\
email address or ORCID}
}

\maketitle

\begin{abstract}
LLVManim is a code visualization tool that generates aesthetically pleasing animations for information control flow and memory allocations. Utilizing the well-supported Manim library alongside LLVM’s built-in static analysis tools and wide language support, LLVManim is able to quickly create informative, professionally styled animations for any code that compiles to LLVM IR. The primary objective of the project is to create an alternative to the unappealing “programmer art” and visual clutter that many standard tools suffer from, instead focusing on an output more suitable for presentations or educational purposes.
\end{abstract}

\begin{IEEEconcepts}
\TODO{non-critical} - https://dl.acm.org/ccs
\end{IEEEconcepts}

\begin{IEEEkeywords}
\TODO{non-critical}
\end{IEEEkeywords}



\section{Introduction}
Despite static analysis and data visualization being among the oldest concepts in computer science, it seems that disappointingly few graphic designers have been significantly interested in the former. While plenty of tools exist for creating control flow graphs or visualizing the stack, the majority of these favor a “function over form” paradigm that focuses on creating light-weight readable output, assuming the user is more concerned with the information than its presentation. This, however, is not always the case: presenting in any context, such as at a conference or school, generally favors quickly digestible and visually interesting content instead of large, static, blocks of text. In these cases, the presenter is currently forced to choose between using the unappealing generated visualization and the slog of creating something presentable for themselves.




\section{Existing Tools}


\subsection{Pythontutor}
\TODO{critical} Examples of \href{https://pythontutor.com/visualize.html}{Pythontutor} functionality \& explain where it lacks


\subsection{LLVM \texttt{dot-cfg} Pass with Graphviz}
\TODO{critical} Same as previous section but for Graphviz. Potentially add subsection explaining LLVM in general.



\section{Manim}
\TODO{critical} Present the Manim library and establish its efficacy with citable references to its effective use in \href{https://www.youtube.com/@3blue1brown}{3Blue1Brown} videos.



\section{LLVManim}
By providing a solution to quickly and easily create data-based animations, LLVManim aims to bridge the gap between these two concepts:
\begin{enumerate}
    \item Methods exist to quickly generate code visualizations, but they are ugly.
    \item The Manim library can make visually impressive animations, but using it is time consuming.
\end{enumerate}
Educators and tech leads alike can rejoice in spicing
up their PowerPoints without needing to
compromise between style and accessibility.


\subsection{Project Goals}
\TODO{critical} Present concrete/quantifiable goals, such as IR instruction coverage and supported customization options, classify features.


\subsection{Implementation Plan}
\TODO{critical} Explain approach and details for how the tool will operate, present UI mock-up.



\section{Projected Timeline}
\TODO{critical} Include a week-by-week schedule of the work you expect to complete. Ensure that each week’s milestone are concrete and measurable so that you know whether you have achieved it. For example, “coding is 50\% done” is not measurable, but “parsing module is complete and tested” is. Don’t forget to allocate time for building your experimental infrastructure. You should think about it deeply enough to be able to give a detailed estimate.



\section{Feedback}
"The figures are helpful for showing how the existing tools work, but for the proposal make sure you show how you want the visualized code to work.  This could be through making a mockup or setting up input for Manim to generate something that looks like what you want.  You should also think about the pipeline for what data you are planning on getting from LLVM, how you are going to get it, and how you will feed it into Manim.

You have figures for some existing tools.  Make sure you talk about them in the proposal and what their limitations are."\\
\TODO{critical} describe any feedback you did NOT take action on, with a brief justification for why (for example, if some other project related to your proposal was suggested, but it is not, this is where you would say why it was not related). Include ALL feedback you have received on the project at any point, whether from the instructor or your peers. If you have addressed every piece of feedback and made changes in response, write “We have addressed all feedback.”



\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.



\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}
