The primary goal of LLVManim is to create a lightweight pipeline for converting
LLVM IR and runtime traces into concise, animated explanations of program
behavior. As a proof-of-concept, the initial version of LLVManim will focus on
visualizing fundamentals, such as control flow and memory allocations.

\textbf{Proof-of-Concept Targets:}
\begin{itemize}
  \item \textbf{User Interface:} Develop a simple command-line interface that allows users to specify input files, select visualization options, and generate animations with minimal configuration.
  
  \item \textbf{LLVM IR Parsing:} Extract control flow and memory access information from LLVM IR, utilizing debug metadata when available.
  
  \item \textbf{Manim Animation Generation:} Translate LLVM IR and trace information into Manim scenes that visually represent control flow, stack frames, heap allocations, and data flow.
    
  \item \textbf{IR Instruction Coverage:} Support for the most common LLVM IR instructions, such as \texttt{load}, \texttt{store}, \texttt{call}, and basic arithmetic operations. This will allow LLVManim to visualize a wide range of simple programs.
    
  \item \textbf{Basic Animation Customization:} Allow users to customize the appearance of animations (e.g. color schemes, animation speed, etc.) to suit different presentation contexts.
  % \item \TODO{non-critical} Come up with more core features.
\end{itemize}

\textbf{Major features (required to realize the intended product):}
\begin{itemize}
  \item \textbf{Advanced Animation Customization:} Allow users to customize more aspects of the animations, such as layout styles, node shapes, or animation effects.
  \item \textbf{Basic Interactive Features:} Implement basic interactivity in the generated animations, such as pausing, stepping through execution, or highlighting specific paths.
  \item \textbf{Trace Event Mapping:} Correctly map $\geq95\%$ of run-time events (loads, stores, branches, calls, returns) to IR locations when debug metadata is present.
  % \item \TODO{non-critical} Come up with more major features.
\end{itemize}

\textbf{Stretch features (nice-to-have if time permits):}
\begin{itemize}
  \item \textbf{GUI:} Create a graphical user interface for users who prefer not to use the command line.
  \item \textbf{Advanced Interactive Features:} Implement advanced interactivity in the generated animations, such as allowing users to click on nodes to see underlying IR code or variable values.
  % \item \TODO{non-critical} Come up with more stretch features.
\end{itemize}

\textbf{Deliverables:}
\begin{itemize}
\item A command-line tool that accepts source files or LLVM IR as input and produces animations as output.
\item A library of reusable Manim scene components for visualizing control flow graphs and memory states.
\item Sample visualizations demonstrating LLVManim on standard programs.
\item Documentation covering installation, usage, and supported IR constructs.
\end{itemize}
