All pipeline stages exhibit linear scaling behavior, confirming that LLVManim can handle realistically sized LLVM IR inputs. Benchmarks use synthetic IR programs with controlled instruction and block counts (median of 5 runs per data point).

Fig.~\ref{fig:pipeline_latency} (Appendix~\ref{app:metrics_figures}) shows the relative wall-clock cost of each pipeline stage for a 50-block CFG. The Ingest stage (\texttt{parse\_module\_to\_events}) dominates at 11.6\,ms, while all Transform stages complete in under 0.25\,ms. Fig.~\ref{fig:parse_scaling} confirms that parse time scales linearly with instruction count---$\Theta(n)$ where $n$ is the number of IR instructions.

The scene-graph construction stages also scale linearly: \texttt{build\_scene\_graph(mode='cfg')} is $\Theta(n_b)$ in block count (Fig.~\ref{fig:cfg_build_scaling}), \texttt{derive\_cfg\_trace} is $\Theta(n_b)$ for linear-chain CFGs and $O(n_b \cdot k)$ in the presence of loops (Fig.~\ref{fig:trace_scaling}), and \texttt{build\_scene\_graph(mode='stack')} exhibits sub-linear growth empirically (Fig.~\ref{fig:stack_build_scaling}).

Peak memory allocation also grows linearly with IR size for both pipelines (Fig.~\ref{fig:memory_scaling}).

\subsection{Reproducibility}
All LLVManim results can be reproduced from the public repository\cite{llvmanim-repo}:

\begin{minted}[
  autogobble,
  frame=single,
  bgcolor=listingbg,
  breaklines=true,
  fontsize=\footnotesize,
]{bash}
git clone https://github.com/BenHoule/LLVManim.git
cd LLVManim
uv sync --dev
# run all 4 quality gates
./scripts/quality-check.sh
# Create coverage and LoC figures.
./uv run python docs/metrics/generate_metrics.py
# Create pipeline latency and scaling figures.
./uv run python docs/metrics/generate_perf_metrics.py
\end{minted}

System requirements: Python 3.12+, \texttt{uv}, Linux packages \texttt{libcairo2-dev} and \texttt{libpango1.0-dev} (for Manim), and optionally \texttt{graphviz} for PNG graph export. See the repository's \texttt{README.md} for detailed setup instructions and troubleshooting tips.
